Painting with Triangles

### 2014-04-22 paper.tex

% - Switch 6.3 and 6.4
\begin{figure*}
    \centering
        \fbox{\includegraphics[width=0.49\textwidth]{images/facezoom}}
        \fbox{\includegraphics[width=0.49\textwidth]{images/facezoomtriangles}}
    \caption{A drawing by an artist that took about 30 minutes, resulting in 9030 triangles.} % \Steve{Can we add number of strokes?}}
    \label{fig:face}
\end{figure*}

@@

>>>>

% - Switch 6.3 and 6.4
\begin{figure*}
    \centering
        \fbox{\includegraphics[width=0.49\textwidth]{images/facezoom}}
        \fbox{\includegraphics[width=0.49\textwidth]{images/facezoomtriangles}}
    \caption{A drawing by an artist that took about 30 minutes, using about 70 strokes, resulting in 9030 triangles.}
    \label{fig:face}
\end{figure*}

@@

\begin{figure*}
    \centering
        \fbox{\includegraphics[width=0.45\textwidth]{images/apple}}
        \fbox{\includegraphics[width=0.45\textwidth]{images/eye}}
    \caption{Two more example paintings exploring different styles.}
    \label{fig:stop}
\end{figure*}
